### 2015-12-01 paper/manuscript.Rnw
second graph initial commit

>>>>

<<>>=
folder <- "../data/redundancy/node/"
node_redundancy <- list.files(folder, full.names = TRUE) %>%
    plyr::ldply(function(x, name){
        y <- read.csv(x) 
        info <- basename(x) %>% 
            stringr::str_sub(end = -5) %>% 
            stringr::str_split("_") %>% 
            unlist()
        y %>%
            dplyr::mutate(net = info[[1]],
                                        type = info[2],
                                        keep = info[3])
    })

g
@
